---
title: "Stat420 Project - House Price Prediction Proposal"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Team
- `Sherrine Vanessa Yuwono, syuwono2`
- `Shawn Patel, sjpatel7`
- `Abhay Singh, abhays3`

## Project Introductory Info

The relationship between house prices and the economy is an important motivating factor for predicting house prices. Housing price trends are not only the concern of buyers and sellers, but it also indicates the current economic situation. 
Therefore, it is important to predict housing prices without bias to help both the buyers and sellers make their decisions. 

## Dataset Info

This project uses an [open source dataset](https://dasl.datadescription.com/datafile/housing-prices-ge19/?_sfm_methods=Multiple+Regression&_sfm_cases=1104+59943) from [DASL Data and Story Library](http://lib.stat.cmu.edu/DASL/), which includes 16 explanatory features for predicting prices and 1,735 entries of housing sales in New York, USA. 
`TODO: Add Sherrine's info`

For our project, we shall be considering the 8 below features as predictors for modeling the `Price` value of the house as the response.

- new.construct  (Factor predictor)
- Fuel Type (Categorical Predictor)
- Heat Type (Categorical Predictor)
- Sewer Type (Categorical Predictor)
- Living Area (in sq Ft, Numerical Predictor)
- Bedrooms (Numerical Predictor)
- Bathrooms (Numerical Predictor)
- Rooms (Numerical Predictor)
 
 `TODO: Add info on predictors (levels)`
 
## Our Goal 
Our goal is to use different combinations of predictors and apply regression models () to predict the house prices in King County, USA. 

We hope to gain insight on which variables impact housing valuation the most significantly, as well as any possible interaction between the attributes on the pricing. Analysis of this dataset may be helpful in the decision process of purchasing or selling properties. Our goal is to get a better sense for comparing properties in the housing market.

## Dataset Preview
`Todo: Update data to factor, categorical and numerical. Also have to limit decimal digits`
```{r HousePrices}
library(readr)
HousePricesData = read_csv("housing-prices-GE19.csv")
summary(HousePricesData)
View(HousePricesData)
```

## Including Plots Of House Price

```{r HousePricesPlot, echo=FALSE}
plot(HousePricesData$Price)
```
